working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-14 Manuscript_draft/Manuscript_draft.Rmd
adding captions to figures

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=2.5,fig.width=6,fig.cap="Average effect size and confidence intervals (95%) of the 9 heterospecific treatments of 50% pollen to the different 10 focal species coloured by family."}

@@

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,fig.margin = TRUE,cache=FALSE,fig.height=9,fig.width=7,fig.cap="Effect sizes for the 10 different species. The different families appear with different colours, when a species was focal was coloured differently from its family."}

>>>>

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=2.5,fig.width=6,fig.cap="The impact of foreign pollen on recipient plant species. Effect sizes (with 95%confidence intervals) of 9 different donor species of heterospecific pollen upon all recipients."}

@@

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,fig.margin = TRUE,cache=FALSE,fig.height=9,fig.width=7,fig.cap="The response of heterospecific pollen upon 10 recipient plant species.  Each panel represents one recipient plant species crossed with 50% mixes of the other 9 species."}

### 2019-03-14 Manuscript_draft/Manuscript_draft.tex
fighting with ggplot legend... no succeed
adding captions to figures

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
\caption{Average effect size and confidence intervals (95\%) of the 9
heterospecific treatments of 50\% pollen to the different 10 focal
species coloured by family.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
\caption{Effect sizes for the 10 different species. The different
families appear with different colours, when a species was focal was
coloured differently from its family.}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
\caption{The impact of foreign pollen on recipient plant species. Effect
sizes (with 95\%confidence intervals) of 9 different donor species of
heterospecific pollen upon all recipients.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
\caption{The response of heterospecific pollen upon 10 recipient plant
species. Each panel represents one recipient plant species crossed with
50\% mixes of the other 9 species.}
\end{figure}
